%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Computer Science - MSc Computer Vision (Distinction - expected avg. 85+\%)} % Degree
    {University College London} % Institution
    {London, UK} % Location
    {Sep. 2021 - Present - Sep. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Relevant Modules: Machine Learning for Visual Computing, Image Processing, Networked Systems, Machine Vision, Computer Graphics, Perception and Interface, Robot Vision and Navigation, and Virtual Environment.}
      \end{cvitems}
    }
    
  \cventry
    {Computer Science - BSc Artifial Intelligence (Distinction - avg. 83\%)} % Degree
    {University of Manchester} % Institution
    {Manchester, UK} % Location
    {Sep. 2018 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Relevant Modules: Mathematics, Operating System, Algorithms and Complexity, Databases, Logic and Modelling, Software Engineering, Imperative Programming, Object-oriented Programming, Machine Learning and Optimization, AI and Games,  Computer Vision, Graphics and Image Processing, Distributed Computing, Mobile System, and Cryptography.}
      \end{cvitems}
    }
    
    \cventry
    {Foundation - Computing (1\textsuperscript{st} in cohort)} % Degree
    {Bellerbys College} % Institution
    {Brighton, UK} % Location
    {Jan. 2018 - Jun. 2018} % Date(s)
    {
     \begin{cvitems} % Description(s) bullet points
        \item {Relevant Modules: Decision \& Pure Maths, Databases, Programming \& Code, Web Design, and System Analysis.}
      \end{cvitems}
    }
    
    % \cventry 
    % {Secondary School - (top 5\%)} % Degree
    % {Bartley Secondary School} % Institution
    % {Bartley, SG} % Location
    % {Jan. 2017 - Oct. 2018} % Date(s)
    % {
    %   \begin{cvitems} % Description(s) bullet points
    %      \item {General study.}
    %   \end{cvitems}
    % }

%---------------------------------------------------------
\end{cventries}
