%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

% ----------------------------------------------------------------

\cventry
    {Software Engineer - Java \& Go} % Job title
    {Cisco} % Organization
    {London, UK} % Location
    {Oct. 2022 - Current} % Date(s)
    {
      % \begin{cvitems} % Description(s) of tasks/responsibilities
      %   \item {Facilitates security policies management in highly distributed environments across cisco network devices.}
      %   \item {Integrates multiple external services/applications in cloud-native environments such as AWS and Azure.}
      %   \item {Simplified user journey on device management platform based on AWS and Azure Vnet by cutting down number of manual onboarding steps and building an automated device migration tool.}
      %   \item {Led the database migration of authentication and authorization service; facilitated a smooth transition from self-deployed database to managed cloud based solution.}
      %   \item {Main contributor of external platform development, responsible for designing and building multiple aws terraform plugin providers from scratch. Examples: https://github.com/CiscoDevNet/terraform-provider-cdo, https://github.com/CiscoDevNet/terraform-aws-cdo-sdc, and https://github.com/CiscoDevNet/terraform-aws-cdo-sec}
      % \end{cvitems}
      \begin{cvitems}
        \item {Enhanced security policy management across Cisco's distributed network devices, optimizing operations in complex environments.}
        \item {Integrated external services in cloud-native environments like AWS and Azure, streamlining functionality and performance.}
        \item {Improved user experience on the AWS and Azure Vnet device management platform by automating onboarding and device migration, reducing manual steps.}
        \item {Successfully led the migration of authentication and authorization services from self-deployed database to cloud-managed solution, ensuring seamless transitions.}
        \item {Drove the development of external platforms, spearheading the design and creation of multiple AWS Terraform plugin providers from inception. Examples: Terraform Provider for Cisco Defense Orchestrator (https://github.com/CiscoDevNet/terraform-provider-cdo), AWS Terraform Provider for Secure Device Connector (https://github.com/CiscoDevNet/terraform-aws-cdo-sdc), and AWS Terraform Provider for Security Services (https://github.com/CiscoDevNet/terraform-aws-cdo-sec).}
    \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Internship - Java} % Job title
    {Amazon} % Organization
    {Cambridge, UK} % Location
    {Jun. 2021 - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % \item {\textit{Alexa is a virtual assistant technology based on cloud voice service. My team is responsible for generating answers to users' questions.}}
        % \item {Built and embedded an experiment framework into the existing question-answering pipeline.}
        % \item {Conducted experiments with 1\% customer traffic, analyzed over 10 GBs of customer responses; and presented a proof-of-concept report for novel answering techniques that received positive feedback.}
        \item {Built and embedded an experiment framework into the existing question-answering pipeline. Conducted experiments with 1\% customer traffic, and presented a highly-rated proof-of-concept report.}
        \item {Developed an efficient workflow for future experiments, and reduced experiment deployment time needed from days to hours.}
        % ; coordinated and discussed design decisions with multiple teams.}
        \item {Received full-time offer.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer Internship - Java} % Job title
    {Amazon} % Organization
    {Edinburgh, UK} % Location
    {Jun. 2020 - Sep. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % \item {\textit{Item Safety is responsible for deciding whether an item in Amazon is safe to promote using ML-based methods.}}
        \item {Developed procedures that aggregate \approx3 billion item records into concise datasets daily using tools based on Spark. Built an effective modern visualization dashboard with these datasets using Elastic Search and Kibana.}
        % \item {Reduced time-consuming ad-hoc graph analysis from minutes to seconds by developing an effective modern visualization dashboard using Elastic Search and Kibana.}
        \item {Developed an API package for automating the creation of visualization components and dashboards.}
        \item {Received full-time offer.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
