%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Sole Developer - HTML/CSS, Javascript, and GLSL} % Role
    {Personal Websites} % Event
    {London, UK} % Location
    {Jun. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written websites from scratch using various technologies such as \href{https://reactjs.org/}{reactJs}, \href{https://nextjs.org/}{nextJs}, \href{https://threejs.org/}{threeJs}, \href{https://sass-lang.com/}{sass},  \href{https://postcss.org/}{postcss}, and \href{https://pugjs.org/api/getting-started.html}{pugJs}.}
        \item Visits \url{https://luoweilue.com} (simple) or \url{https://weilueluo.com} (fancy).
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Sole Developer - Python} % Role
    {Machine Learning with Pytorch} % Event
    {London, UK} % Location
    {Nov. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s)
      \item {\textbf{Workflow Enhancement} Implement a number of ML models to aid artists development process for an 2D animation company based in London (ongoing master project, not allowed to disclose).}
        \item {\textbf{Time Series Prediction} Generate Monophonic and Polyphonic piano music via various models \& techniques, including LSTM, skip connection \& attention. Report can be found at \href{https://github.com/Redcxx/Third-Year-Project-Report}{\textit{https://github.com/Redcxx/Third-Year-Project-Report}} and music samples can be found at \href{https://soundcloud.com/kallzvx/sets}{\textit{https://soundcloud.com/kallzvx/sets}}.}
        \item {\textbf{Image Classification} Transfer learning based on a pre-trained resnet, over 90\% accuracy with 10 classes of 1000 training samples.}
      \end{cvitems}
    }
    
  %---------------------------------------------------------
  \cventry
    {Lead Developer - C\#} % Role
    {First Person Virtual Reality Game - Bouncing Ray} % Event
    {London, UK} % Location
    {Mar. 2022 - Apr. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Lead a team of 4 to build a first person Virtual Reality game based on the ubiq framework (\href{https://github.com/UCL-VR/ubiq}{\textit{https://github.com/UCL-VR/ubiq}}). Project can be found at \href{https://github.com/HengyiWang/COMP0113-BouncingRay}{\textit{https://github.com/HengyiWang/COMP0113-BouncingRay}}.}
      \end{cvitems}
    }
  
  \cventry
    {Sole Developer - Python} % Role
    {Local Nameserver} % Event
    {London, UK} % Location
    {Feb. 2022 - Mar. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Written a local nameserver that able to resolve any IPv4 address according to \href{https://datatracker.ietf.org/doc/html/rfc1034}{RFC 1034} and \href{https://datatracker.ietf.org/doc/html/rfc1035}{RFC 1035} specification. Project can be found at \href{https://github.com/Redcxx/local-nameserver}{\textit{https://github.com/Redcxx/local-nameserver}}.}
      \end{cvitems}
    }
    
  \cventry
    {Sole Developer - Python} % Role
    {Poisson Image Editing} % Event
    {London, UK} % Location
    {Dec. 2021 - Jan. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Implemented the \href{https://www.cs.jhu.edu/~misha/Fall07/Papers/Perez03.pdf}{Poisson Image Editing paper}. Including techniques such as naive filling; import \& mixing gradient; texture flattening, colour isolation \& illumination.  Project can be found at \href{https://github.com/Redcxx/poisson-image-editing}{\textit{https://github.com/Redcxx/poisson-image-editing}}.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sole Developer - Python} % Role
    {Image Downloader} % Event
    {Manchester, UK} % Location
    {Jun. 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Designed and implemented an API supports automatic login, multi‑threading downloading, various format parsing and filter images, along with a graphical user interface. See \href{https://github.com/Redcxx/Pikax}{\textit{https://github.com/Redcxx/Pikax}}.}
      \end{cvitems}
    }
    
  \cventry
    {Sole Developer} % Role
    {Other} % Event
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {More projects can be found at my github \href{https://github.com/Redcxx}{https://github.com/Redcxx}.}
      \end{cvitems}
    }
  
    


%---------------------------------------------------------
\end{cventries}
